Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-03-03 docs/00-manuscripts/ieee/ieee-manuscript.tex
Update ieee-manuscript.tex

To use the full potential of the hyperspectral data, all possible vegetation indices supported by the R package hsdar (89 in total) as well as all possible \ac{NRI} combinations were calculated.

NRIs follow the \ac{OMNBR} concept of data-driven information extraction from narrow-band indices of hyperspectral data \cite{thenkabail2000,thenkabail2018}.
In principal any index can be used for this data-driven concept.
Due to the popularity of the NDVI index in vegetation applications and the availability of this index in the \texttt{nri()} function of the \texttt{hsdar} R package, the following formula was applied to every available band combination:

@@

\noindent
with \(i\) and \(j\) being the respective band numbers.

>>>>

To use the full potential of the hyperspectral data, all possible vegetation indices supported by the R package hsdar (89 in total) as well as all possible \ac{NRI}s were calculated.

NRIs follow the \ac{OMNBR} concept of data-driven information extraction from narrow-band indices of hyperspectral data \cite{thenkabail2000,thenkabail2018}.
While various index formulations such as band ratios or normalized ratios are available, indices involving the same bands are strongly correlated.
Since the widely-used NDVI index belongs to the family of normalized ratio indices (NRIs), which are implemented in the \texttt{hsdar} R package, we used the following NDI formula to combine all pairs of reflectances:

@@

\noindent
where \(i\) and \(j\) are the respective band numbers.
